Supplementary Content

### 2022-03-16 experiments/2_supplement/supplement.Rmd

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
